---
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)

library(dplyr)
library(leaflet)
library(magrittr)
library(sf)
library(shiny)
library(shinydashboard)
```

## Airport

We expect most travelers will be flying into [AUS airport](https://www.austintexas.gov/airport), located in southeast Austin. AUS serves all major US airlines. 

The wedding venue is an approximately 40 minute drive west from the airport. For those looking to spend a bit of time in the city before the wedding, downtown is about a 15 minute drive.

<br>

## Getting around

### Rental cars

All standard options for rental cars are available at the AUS airport. As an alternative, we also encourage you to check out the service [Turo](https://www.turo.com), which is essentially an "AirBnB for cars". We've found this service to be very reliable and often cheaper than renting from a company.

### Uber and Lyft

AUS airport is served by both Uber and Lyft. In our experience, Lyft tends to be cheaper, but we encourage rideshare users to check both.

Please note that if you intend to use rideshare to travel to and from the venue, **we strongly advise that you schedule your rides in advance.** The venue is in a rural enough area that on-demand rides -- especially late at night when the wedding ends -- may be hard to come by. Scheduling your ride in advance will guarantee you are not stuck at the venue when the party is over.

### Shuttle

As there is no central hotel block, we are unable to offer shuttle service to/from the venue. Please ensure to arrange your own transportation to the event; if you have any questions, please reach out to Aaron or Steph.

### Public transit

This wouldn't be an Aaron-made website if I didn't talk about buses right?

Unfortunately, public transit does not run from Austin to Spicewood; you will need to either rent a car or use rideshare. However, for those spending time in the city before or after the wedding, public transit is an option for getting around. 

For those wanting to use transit from the airport, the #20 bus is about a 25 minute ride to downtown. It picks up every 30 minutes from 6:00am to 7:00am, every 15 minutes from 7:00am to 8:00pm, and every 30 minutes from 8:00pm to 11:30pm, every day of the week.

For more information, or for information on other routes, check out the [CapMetro site.](https://www.capmetro.org/)

<br>

## Lodging

### Hotels

There is no hotel block for the wedding -- of the few hotels in the area of our venue, none offer blocks at a discounted rate. If you choose to stay in a hotel, the most convenient ones are all about 20 minutes east of the venue in the Lakeway/Bee Cave area (about halfway between Austin and the venue):

- Hampton Inn and Suites Austin - Lakeway: 2013 Ranch Rd 620 S, Lakeway, TX 78734. A 20 minute drive from the venue. [(hotel website)](https://www.hilton.com/en/hotels/auslwhx-hampton-suites-austin-lakeway/)

- Holiday Inn Express and Suites Austin NW - Lakeway: 15707 Oak Grove Blvd, Lakeway, TX 78734. A 23 minute drive from the venue. [(hotel website)](https://www.ihg.com/holidayinnexpress/hotels/us/en/lakeway/ausog/hoteldetail)

- La Quinta Inn and Suites by Wyndham Lakeway: 1943 Medical Dr, Lakeway, TX 78734. A 23 minute drive from the venue. [(hotel website)](https://www.wyndhamhotels.com/laquinta/lakeway-texas/la-quinta-inn-and-suites-lakeway/overview)

- Mountain Star Hotel: 3573 Ranch Rd 620 S, Austin, TX 78738. An 18 minute drive from the venue. [(hotel website)](https://mountainstarlodge.com/)

- Springhill Suites Austin West/Lakeway: 322 Medical Pkwy, Lakeway, TX 78738. A 19 minute drive from the venue. [(hotel website)](https://www.marriott.com/en-us/hotels/auswl-springhill-suites-austin-west-lakeway/overview/)

### Other lodging options

One reason we chose Cypress Valley to host our wedding is because of the beauty of the Texas Hill Country! This area is set in beautiful natural surroundings, and is home to some truly excellent breweries and wineries. To take full advantage of this special place, we strongly encourage you to use AirBnB, VRBO, or other services to find some of the unique stays available around our venue. Domes, cabins, and even waterfront homes on the Colorado River are possibilities in this area!

<br>

## Map

See the map below for an alignment of key locations.

```{r Config}
travel = c(
  30.20489947767981, -97.66714222969232, #AUS
  30.42103456773607, -98.10553983419227  #Cypress Valley
) %>%
  matrix(
    ncol = 2,
    byrow = TRUE
  ) %>%
  data.frame() %>%
  setNames(
    c("Y","X")
  ) %>%
  mutate(
    name = c("AUS","Cypress Valley")
  ) %>%
  st_as_sf(
    coords = c("X","Y"),
    crs = 4326
  ) %>%
  mutate(
    label = paste0(
      "<b>", name, "</b>" 
    )
  )
```

```{r Map, out.width = '100%'}
get_travel_icon = function(df){
  sapply(df$name, function(name){
    if(name == "AUS"){
      "plane"
    } else if(name == "Cypress Valley"){
      "tree"
    } else{
      "hotel" #everything else will be a hotel
    }
  }) %>%
    unname()
}
travel_icons = awesomeIcons(
  icon = get_travel_icon(df=travel),
  library = 'fa',
  iconColor = "#FFFFFF",
  markerColor = "darkgreen"
)
center_pt = travel %>%
  st_union() %>%
  st_centroid() %>%
  st_coordinates() %>%
  unname() %>%
  as.vector()
leaflet(travel) %>%
  addProviderTiles("Esri.WorldStreetMap") %>%
  addAwesomeMarkers(
    icon = travel_icons,
    label = ~lapply(label, HTML)
  ) %>%
  setView(
    lng = center_pt[1],
    lat = center_pt[2],
    zoom = 10
  )
```
